The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex
intro words and formatting

@@

\widowpenalty=1000
\clubpenalty=1000

@@

In this \paper, we develop a systematic method for reliably discovering the
transits of large long-period companions in photometric time series
\emph{without human intervention}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission and produce a catalog of discoveries.

@@

\newpage
\appendix

@@

>>>>

\usepackage{endnotes}
\let\footnote=\endnote

@@

\widowpenalty=100000
\clubpenalty=100000

@@

In this \paper, we develop a systematic method for reliably discovering the
transits of large long-period companions in photometric time series
\emph{without human intervention}.
Since the search methodology is fully automated, we can robustly measure the
search completeness~--~using injection and recovery tests~--~and use these
products to place probabilistic constraints on the occurrence rate of
long-period planets.
We apply this method to a subset of the archival data from the \kepler\
Mission, release a catalog of exoplanet candidates, and estimate the
occurrence rate of long-period exoplanets.
We finish by discussing the potential effects of false positives, the
prospects for radial velocity follow-up of these candidates, and compare to
calculated occurrence rate to results based on discoveries using different
planet discovery methods.

@@

\appendix

@@

\theendnotes
